%\documentclass{resume} % Use the custom resume.cls style
\documentclass{article}
\usepackage{parskip} % So that all paragraphs are class ``noindent'' in the generated .html file
\usepackage[none]{hyphenat} % No hypens at line breaks anywhere
\raggedright % Only left justified

\begin{document}

I am interested in analyzing large datasets to better understand, model, and predict the core relationships in those datasets.
I specialize in modeling human behavioral data, but I also have experience modeling physics-based systems,
so I've applied the same core analytic and mathematical approach to modeling systems across a broad range of domains.

I also have almost a decade of HPC experience, so I know how to optimize code, and accelerate the research pace by speeding up the turnaround time to finish the various steps in the data analysis process. 
From 2009-2012 I was part of the small development team that completely redesigned and rewrote the MindModeling volunteer distributed HPC system (uses BOINC and technology similar to Folding@HOME).
That web-based system is currently being used by cognitive scientists within the department of defense to better explore the entire performance space of their cognitive models.

From 2012-2014 my dissertation work is focused on evaluating and improving models of declarative memory on large-scale datasets.
I am using these models of long term memory to predict the tags and hashtags that authors use on StackOverflow and Twitter when creating content.
This work has required a lot of data mining and data science techniques: proper tokenization of unstructured text, local optimization using a single high-performance workstation, R, data.table, PostgreSQL, and others.

I passionate about using data to build models that are customized to each user's needs, and can anticipate user behavior.
But I am also passionate about building the proper infrastructure and tools so that the process of exploring and modeling the data can be accelerated.
It's great when data can be used to build more intuitive, responsive, and usable systems.
But it's even better when those improvements can be discovered and implemented at a rapid pace.

Thank you for considering me for the position,
-Clayton Stanley

\end{document}
