%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{John Smith} % Your name
\address{123 Broadway \\ City, State 12345} % Your address
\address{(000)~$\cdot$~111~$\cdot$~1111 \\ john@smith.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Rice University} \hfill {\em May 2009} \\ 
M.A. in Psychology with emphasis in computational cognitive modeling \\
Thesis title: Visual Displays: Developing a Computational Model Explaining the Global Effect \\
Advisor: Dr. Mike Byrne \\
Overall GPA: FIXME 

{\bf United States Air Force Academy} \hfill {\em May 2007} \\ 
B.S. in Physics with emphasis in applied physics and computational methods \\
Distinguished Graduate \\
Overall GPA: FIXME
\end{rSection}

%----------------------------------------------------------------------------------------
%	Awards SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards}
\item Awarded United States Air Force Commendation Medal \hfill {\em May 2012}
\item Received 'Kenneth R. Laughery Award', best master’s thesis in Psychology, Rice University \hfill {\em May 2009}
\item Awarded 'Outstanding Cadet in Applied Physics', United States Air Force Academy \hfill {\em May 2007}
\item Won 'Cadet Inter-Service Computer Programming Competition', USAFA \hfill {\em May 2007}
\end{rSection}

\begin{rSection}{Research Interests}
Human Computer Interaction, Analysis of Large-Scale Human Datasets, Human Data Modeling
\end{rSection}

%----------------------------------------------------------------------------------------
%	Experience SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Rice University, Computer Human Interaction Laboratory}{May 2012 - Aug 2012}{Research Programmer}{Houston, TX}
\item Migrated lab's Macintosh Common Lisp GUI code to Clozure Common Lisp. 
\item Implemented the necessary subset of Digitool's MCL GUI specification for Clozure Common Lisp, so all MCL GUI code could be compiled by Clozure Common Lisp without any code modifications.
\item Heavy use of Clozure's Objective-C / Cocoa bridge, CLOS and extending Clozure's easygui class, multiple inheritance / mixins, read- and compile-time macros.
\end{rSubsection}

\begin{rSubsection}{Air Force Research Laboratory, Cognitive Models and Agents}{May 2009 - May 2012}{Software Engineer and Cognitive Scientist}{Dayton, OH}
\item Member of development team for the net-centric MindModeling volunteer computing research project.
Part of development team of 3 that designed and implemented a complete redesign of the system between 2010-2011.
Multi-programming-language project; 10,000+ LOC.
\item Built a generic wrapper that allows modelers with lisp and non-lisp models to easily
(within minutes) interface their model in a form that is compatible with High Performance Computing and Distributed Computing clusters.
Tool (called LETF) is ~1500 lines of common-lisp. Successfully transitioned the codebase to the rest of the team before departure.
\item Built a tool that automatically hardens \& certifies OS X and OpenSUSE machines to be used on our Air Force research network.
Written in Bash and Makefile.
Being used in a production environment, and other labs are now using and contributing to the codebase.
\end{rSubsection}

\begin{rSubsection}{Rice University, Computer Human Interaction Laboratory}{May 2007 - May 2009}{Graduate Student}{Houston, TX}
\item Explored the underlying mechanisms involved in producing various phenomena found in visual search tasks
(e.g., distractor ratio effect, global effect) through modeling empirical data using the ACT-R cognitive architecture. 
\end{rSubsection}

\begin{rSubsection}{United States Air Force Academy, Department of Physics}{May 2006 - May 2007}{Research Assistent}{Colorado Springs, CO}
\item Helped research, restructure, and reprogram a parallelized lightcurve inversion program developed in Matlab.
Successfully ported and run on Hoku (Cray XD-1 Linux computing system), located at MHPCC.
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & 		Common Lisp, GNU Make, Bash, Regex, R, Matlab, PHP, \\
& 				SQL, Python \\
Programming Paradigms &		Macros, Anaphoric/Read/Compile Macros, DSL programming, \\
& 				object oriented, functional, HOFs, closures, declarative, \\
&				code parallelization \& optimization \\
Protocols \& APIs & 		ACT-R, Cocoa, BOINC, Clozure's Objective C bridge \\
Databases &			PostgreSQL, MySQL \\
Networking \& Infrastructure &	VMWare virtualization technologies, SAN configuration, \\
&				Network Services: Apache, SQL, VNC, sshd, Samba \\
Tools & 			git, Vim, command-line, High-Performance Computers, \\
&				Jenkins, \LaTeX, FogBugz \\
Team Processes & 		Agile, Scrum, daily standups, restrospectives, code reviews, \\
& 				bug tracking, test-driven development \\
Relevant Coursework &		Statistics: univariate, multivariate, psychometrics, regression \\
&				Mathematics: e.g., partial differential equations, discrete math
\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
