%----------------------------------------------------------------------------------------
%	Experience SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Rice University, Computer Human Interaction Laboratory}{May 2012 - Aug 2012}{Research Programmer}{Houston, TX}
\item Migrated lab's Macintosh Common Lisp GUI code to Clozure Common Lisp. 
\item Implemented the necessary subset of Digitool's MCL GUI specification, so all MCL GUI code could be compiled by Clozure Common Lisp without any code modifications.
\item Heavy use of Clozure's Objective-C / Cocoa bridge, CLOS and extending Clozure's easygui class, multiple inheritance / mixins, read- and compile-time macros.
\end{rSubsection}

\begin{rSubsection}{Air Force Research Laboratory, Cognitive Models and Agents}{May 2009 - May 2012}{Software Engineer and Cognitive Scientist}{Dayton, OH}
\item Developer for the net-centric MindModeling volunteer computing research project.
Part of small (3 person) development team that redesigned and reimplemented the entire system between 2010-2011.
Systems-level project. 10,000+ SLOC. 10+ programming languages.
\item Built a generic wrapper in Common Lisp that allows modelers to easily
(within minutes) interface their model in a form that is compatible with High Performance and Distributed Computing clusters.
Codebase is used on MindModeling system.
Successfully transitioned the code to team before departure.
\item Built a tool in Bash and GNU Make that automatically hardens \& certifies OS X and OpenSUSE machines to be used on the Air Force research network.
Deployed to a production environment and transitioned codebase prior to departure.
\end{rSubsection}

\begin{rSubsection}{Rice University, Computer Human Interaction Laboratory}{May 2007 - May 2009}{Graduate Student}{Houston, TX}
\item Explored the mechanisms involved in producing various phenomena found in visual search tasks
(e.g., distractor ratio effect, global effect) through modeling with the ACT-R cognitive architecture. 
\end{rSubsection}

\begin{rSubsection}{United States Air Force Academy, Department of Physics}{May 2006 - May 2007}{Research Assistent}{Colorado Springs, CO}
\item Helped research, restructure, and reprogram a parallelized lightcurve inversion program developed in Matlab.
Successfully ported and run on Hoku (Cray XD-1 Linux system), located at MHPCC.
\end{rSubsection}

%------------------------------------------------

\end{rSection}
