%----------------------------------------------------------------------------------------
%	Experience SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

  \begin{rSubsection}{Bloomberg LP, UX Design}
    {Jan 2015 - Present}{UX Data Scientist}{New York, NY}
  \item Applying statistical methods to telemetry data to improve the design of the Terminal.
  \item Working with engineering to build a next-generation analytics platform.
  \item Working with engineering to improve and expand current instrumentation.
  \item Working with engineering to build self-service analytics tools for designers and product managers.
  \item Working with user experience researchers to design and analyze quantitative experimental studies.
  \end{rSubsection}

  \begin{rSubsection}{Rice University, Computer Human Interaction Laboratory}
    {Aug 2012 - Dec 2014}{Graduate Research Assistant}{Houston, TX}
  \item Evaluated and improved declarative memory models using large-scale behavioral datasets.
    Explored Bayesian and vector-based tag classifiers to predict user-generated tags on StackOverflow and Twitter.
  \end{rSubsection}

  \begin{rSubsection}{Rice University, Computer Human Interaction Laboratory}
    {May 2012 - Aug 2012}{Research Programmer}{Houston, TX}
  \item Migrated 50K lines of Macintosh Common Lisp (MCL) GUI code to Clozure Common Lisp (CCL).
    Implemented subset of the MCL GUI specification in CCL, so that CCL could run original MCL code.
  \item Consequently, provided a 10-100x speedup in code run time, and allowed modelers to use the newest OS X operating system and improved IDEs during development.
  \end{rSubsection}

  \begin{rSubsection}{Air Force Research Laboratory, Cognitive Models and Agents}
    {May 2009 - May 2012}{Cognitive Scientist and Software Engineer}{Dayton, OH}
  \item 
    Enabled Teraflops of free computing power for the AF.
    Developer for the net-centric MindModeling volunteer computing research project.
    Part of core dev team that redesigned and reimplemented the entire system between 2010-2011.
    Systems-level project. 10,000+ SLOC. 10+ programming languages. 
  \item
    Led first organization in AFRL headquarters to certify and connect to the Defense Research Engineering Network (DREN).
  \item
    Wrote a system-hardening tool for Linux and OS X to certify machines for the DREN.
  \end{rSubsection}

  \begin{rSubsection}{Rice University, Computer Human Interaction Laboratory}
    {May 2007 - May 2009}{Graduate Research Assistant}{Houston, TX}
  \item Improved and validated a cognitively-plausible and computationally-efficient theory of visual search, 
    and implemented the model in the ACT-R cognitive architecture.
  \end{rSubsection}

  \begin{rSubsection}{United States Air Force Academy, Department of Physics}
    {May 2006 - May 2007}{Undergraduate Research Assistant}{Colorado Springs, CO}
  \item Researched, redesigned, and reimplemented a parallelized lightcurve inversion program developed in Matlab.
    Successfully ported and run on Hoku (Cray XD-1 Linux system), located at MHPCC.
  \end{rSubsection}

%------------------------------------------------

\end{rSection}
